### 2020-09-15 paper/methods.tex
After Osama's edits

The Chinese Academy of Sciences started the program of Thorium Molten Salt Reactor (TMSR) in 2011 \cite{jiang2012advanced}, and many works have been done on the design of MSR and the use of Thorium with the Th-U fuel cycle \cite{li2015analysis}. Among them, the SD-TMSR is proposed in 2018 \cite{li_optimization_2018}, which is a graphite-moderated molten salt reactor with thermal power of 2,250 MW$_{th}$. The design of the SD-TMSR is inspired by the \gls{MSBR} \cite{robertson_conceptual_1971} and the \gls{TMSR} \cite{nuttin2005potential}, which combines the advantages of high breeding ratio (BR) in fast spectrum and low fissile inventory of $^{233}$U in thermal spectrum. The SD-TMSR also offers a negative and strong temperature coefficient of reactivity \cite{li_optimization_2018}. Figure~\ref{fig:ff} illustrates the quarter-core view of the
SD-TMSR. The core of the 
SD-TMSR is a right cylinder divided into an inner zone (486 fuel tubes) 
and an outer zone (522 fuel tubes) to enhance breeding performance.
\begin{figure} % replace 't' with 'b' to \centering [hbp!]
	\includegraphics[width=\textwidth]{ff.png}
	\caption{$XZ$ (a) and $XY$ (b) section of the quarter-core model of the 
		SD-TMSR \cite{ashraf2019Preliminary}.}
	\label{fig:ff}
\end{figure}
In this study, the fuel salt composition is LiF-BeF$_2$-(HM)F$_N$ (70-17.5-12.5 mol\%),
where HM is the heavy metal (i.e., $^{232}$Th and fissile 
materials), and $N$ depends on the chosen fissile material and the 
thermochemical state of the liquid fuel salt. Three different types of initial 
fissile materials are considered: (1) $^{233}$U \cite{ashraf2020whole}, 
(2) reactor-grade Pu \cite{marka1993explosive}, and (3) transuranic (TRU) 
elements from \gls{LWR} \gls{SNF} \cite{de2000scenarios}.
The density and volume of the fuel salt are 3.3 g/cm$^{3}$ and 52.9 m$^3$, 
respectively. The liquid fuel salt circulates continuously through the channels
that pierce the graphite hexagonal prisms. The core is surrounded by 
axial and radial graphite reflectors to minimize the neutron leakage.
We adopted the same graphite density reported in the original SD-TMSR paper (2.3 g/cm$^3$) \cite{li_optimization_2018} to be consistent with results in the literature.
A 10-cm-thick B$_4$C cylinder surrounds the core to shield against neutrons and heat.
Finally, the SD-TMSR pressure vessel holds all reactor components and is made of 
a Hastelloy N alloy. The main characteristics of the SD-TMSR are 
summarized in Table~\ref{tab:table1}.

@@

The assessment of the optimal absorber radius should be an important consideration. If the CR radius is too large, the absorber material is not effectively utilized, due to self-shielding. We changed the radius of the CR and calculated the corresponding $k_{eff}$ when all CRs were fully inserted. Figure~\ref{fig:Radius} illustrates the change of the $k_{eff}$ with the radius of the B$_4$C control rod. As shown in Figure~\ref{fig:Radius}, in the region between 0 and 0.75 cm, the $k_{eff}$ decreases sharply with increasing absorber radius. However, in the region between 0.75 and 1.0 cm, there is almost no change in the $k_{eff}$. This is because of the geometry self-shielding of the neutron flux; beyond r = 0.75 cm, the $^{10}$B atoms in the central zone of the CR have relatively low chance for neutron capture.
From the obtained results, we proposed the control rod as a cylinder with a radius of 0.75 cm and a height of 520 cm (core height in addition to upper and lower plenums).
The absorbing material is surrounded by a 0.25-cm-thick cladding made of AIM1 
(15Cr-15Ni) steel alloy \cite{SERAN2017285} and the guide tube is made of 
SiC structural material (see Figure~\ref{fig:cr}). We simulated a 0.1-cm-thick gap between the 
cladding and guide tube to facilitate the control rod movement. However, the absorber-cladding gap was neglected for simplicity.
All densities of rod materials are listed in
Table~\ref{tab:table111}.

@@

The excess reactivity $\rho$$_e$ is the reactivity of the core when all control rods are withdrawn. $\rho$$_e$ is calculated by SERPENT-2 in \$ units based on equation~\ref{Equ:1}, where $k_{eff}$ is the effective multiplication factor of the core and $\beta_{eff}$ is the effective fraction of delayed neutrons:

\begin{equation}
\label{Equ:1}
{{\rho}_{e}}=\dfrac{{k_{eff}}-1}{{k_{eff}}{{\beta}_{eff}}}.
\end{equation}

The effective delayed neutron fraction is calculated by the adjoint-weighted time constants using a perturbation technique in SERPENT-2 \cite{leppanen2014calculation}, and it accounts for the steady-state of the fuel salt.

@@

The control rod worth (CRW) is the amount of negative reactivity associated with the control rod insertion. The CRW is calculated by SERPENT-2 in \$ units based on equation~\ref{Equ:2}, where $\Delta\rho$$_{CRi}$ is the worth of the i$^{th}$ control rod (CR), $\rho$$_e$ is the initial excess reactivity, and $\rho$$_{CRi}$ is the excess reactivity after insertion of the i$^{th}$ CR \cite{vcerba2017optimization}:

@@

The integral CRW is the total reactivity change due to the full 
insertion or withdrawal of the CR. However, the \textit{differential CRW} is the
reactivity inserted per unit of withdrawal [\$/cm]. To calculate those 
parameters, we varied the position of CR clusters from fully withdrawn to 
fully inserted. Equation~\ref{Equ:4} is used to calculate the integral CRW 
[\$], where $k_{j-1}$ and $k_{j}$ are the effective multiplication factors 
before and after CR insertion to the $j$$^{th}$ step, respectively, $\beta_{j}$ is the
fraction of delayed neutrons at the $j$$^{th}$ step, and $N$ is the number of steps:

\begin{equation}
\label{Equ:4}
{{\Delta}{\rho}_{j}}=\sum_{j=1}^{N}\dfrac{{k_{j}}-{k_{j-1}}}{{{k_{j}}{k_{j-1}}}{{\beta}_{j}}}.
\end{equation}

@@

\begin{equation}
\label{Equ:5}
\dfrac{{\partial}{\rho}_{j}}{{\partial{Z}}}=\dfrac{1}{{\Delta}{Z}}\dfrac{{k_{j}}-{k_{j-1}}}{{{k_{j}}{k_{j-1}}}{{\beta}_{j}}}.
\end{equation}

>>>>

The Chinese Academy of Sciences started the program of Thorium Molten Salt Reactor (TMSR) in 2011 \cite{jiang2012advanced}, and many works have been done on the design of MSR and the use of Thorium with the Th-U fuel cycle \cite{li2015analysis}. Among them, the SD-TMSR is proposed in 2018 \cite{li_optimization_2018}, which is a graphite-moderated molten salt reactor with thermal power of 2,250 MW$_{th}$. The design of the SD-TMSR is inspired by the \gls{MSBR} \cite{robertson_conceptual_1971} and the \gls{TMSR} \cite{nuttin2005potential}, which combines the advantages of high breeding ratio (BR) in fast spectrum and low fissile inventory of $^{233}$U in thermal spectrum. The SD-TMSR also offers a negative and strong temperature coefficient of reactivity \cite{li_optimization_2018}. Figure~\ref{fig:ff} illustrates the quarter-core view of the
SD-TMSR. The core of the 
SD-TMSR is a right cylinder divided into an inner zone (486 fuel tubes) 
and an outer zone (522 fuel tubes) to enhance breeding performance.
\begin{figure} % replace 't' with 'b' to \centering [hbp!]
	\includegraphics[width=\textwidth]{ff.png}
	\caption{$XZ$ (a) and $XY$ (b) section of the quarter-core model of the 
		SD-TMSR \cite{ashraf2019Preliminary}.}
	\label{fig:ff}
\end{figure}
In this study, the fuel salt composition is LiF-BeF$_2$-(HM)F$_N$ (70-17.5-12.5 mol\%),
where HM is the heavy metal (i.e., $^{232}$Th and fissile 
materials), and $N$ depends on the chosen fissile material and the 
thermochemical state of the liquid fuel salt. Three different types of initial 
fissile materials are considered: (1) $^{233}$U \cite{ashraf2020whole}, 
(2) reactor-grade Pu \cite{marka1993explosive}, and (3) transuranic (TRU) 
elements from \gls{LWR} \gls{SNF} \cite{de2000scenarios}.
The reactor-grade Pu and TRU isotopic vectors are summarized in 
Table~\ref{tab:table52} and ~\ref{tab:table53}, respectively.

\begin{table} % [!ht]
	\centering
	\caption{Reactor-grade Pu vector (wt.\%) \cite{marka1993explosive}.}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{X X X X X}
		\hline
		$^{238}$Pu & $^{239}$Pu & $^{240}$Pu & $^{241}$Pu & $^{242}$Pu \\
		\hline
		$ $ $ $ $ $ $ $ $ $1.3 &$ $ $ $ $ $60.3&$ $ $ $ $ $24.3&$ $ $ $ $ $ $ $ $ $9.1&$ $ $ $ $ $ $ $ $ $ $ $ $ $5 \\
		\hline
	\end{tabularx}
	\label{tab:table52}
\end{table}

\begin{table} %  [!ht]
	\centering
	\caption{TRU vector (wt.\%) \cite{de2000scenarios}.}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{X X X X X X X X X X}
		\hline
		$^{237}$Np&$^{238}$Pu & $^{239}$Pu & $^{240}$Pu & $^{241}$Pu & $^{242}$Pu&$^{241}$Am &$^{243}$Am&$^{244}$Cm &$^{245}$Cm\\
		\hline
		$ $ $ $ $ $ $ $ $ $6.3&$ $ $ $ $ $ $ $ $ $2.7& $ $ $ $ $ $45.9& $ $ $ $ $ $21.5& $ $ $ $ $ $10.7&$ $ $ $ $ $ $ $ $ $6.7&$ $ $ $ $ $ $ $ $ $3.4&$ $ $ $ $ $ $ $ $ $1.9&$ $ $ $ $ $ $ $ $ $$ $0.8&$ $ $ $ $ $ $ $ $ $0.1 \\
		\hline
	\end{tabularx}
	\label{tab:table53}
\end{table}

The density and volume of the fuel salt are 3.3 g/cm$^{3}$ and 52.9 m$^3$, 
respectively. The liquid fuel salt circulates continuously through the channels
that pierce the graphite hexagonal prisms. The core is surrounded by 
axial and radial graphite reflectors to minimize the neutron leakage.
We adopted the same graphite density reported in the original SD-TMSR paper (2.3 g/cm$^3$) \cite{li_optimization_2018} to be consistent with results in the literature.
A 10-cm-thick B$_4$C cylinder surrounds the core to shield against neutrons and heat.
Finally, the SD-TMSR pressure vessel holds all reactor components and is made of 
a Hastelloy N alloy. The main characteristics of the SD-TMSR are 
summarized in Table~\ref{tab:table1}.

@@

The assessment of the optimal absorber radius should be an important consideration. If the CR radius is too large, the absorber material is not effectively utilized, due to self-shielding. We changed the radius of the CR and calculated the corresponding $k_{eff}$ when all CRs were fully inserted. Figure~\ref{fig:Radius} illustrates the change of the $k_{eff}$ with the radius of the control rod for all different materials. As shown in Figure~\ref{fig:Radius}, in the region between 0.0 and 0.75 cm, the $k_{eff}$ decreases sharply with increasing absorber radius for all absorbers. However, for the B$_4$C control rod, in the region between 0.75 and 1.0 cm, there is almost no change in the $k_{eff}$. This is because of the geometry self-shielding of the neutron flux; beyond r = 0.75 cm, the $^{10}$B atoms in the central zone of the CR have relatively low chance for neutron capture. Other absorbers not significantly affected by the self-shielding phenomenon in the region of study (0.0$<$r$<$1.0 cm). From the obtained results, we proposed the control rod as a cylinder with a radius of 0.75 cm and a height of 520 cm (core height in addition to upper and lower plenums).
The absorbing material is surrounded by a 0.25-cm-thick cladding made of AIM1 
(15Cr-15Ni) steel alloy \cite{SERAN2017285} and the guide tube is made of 
SiC structural material (see Figure~\ref{fig:cr}). The thickness of the gap between the CR and graphite in MSBR is about 7\% of the CR diameter \cite{robertson_conceptual_1971}, thus, we simulated a 0.1-cm-thick gap ($\sim$7\% of the CR diameter) between the cladding and guide tube to facilitate the control rod movement. However, the absorber-cladding gap was neglected for simplicity. Thermal emission calculations is out of scope and also neglected in this study. All densities of rod materials are listed in
Table~\ref{tab:table111}.

@@

The excess reactivity $\rho$$_e$ is the reactivity of the core when all control rods are withdrawn. $\rho$$_e$ is calculated by SERPENT-2 based on equation~\ref{Equ:1}, where $k_{eff}$ is the effective multiplication factor of the core:

\begin{equation}
\label{Equ:1}
{{\rho}_{e}}=\dfrac{{k_{eff}}-1}{{k_{eff}}}.
\end{equation}

@@

The control rod worth (CRW) is the amount of negative reactivity associated with the control rod insertion. The CRW is calculated by SERPENT-2 based on equation~\ref{Equ:2}, where $\Delta\rho$$_{CRi}$ is the worth of the i$^{th}$ control rod (CR), $\rho$$_e$ is the initial excess reactivity, and $\rho$$_{CRi}$ is the excess reactivity after insertion of the i$^{th}$ CR \cite{vcerba2017optimization}:

@@

The integral CRW is the total reactivity change due to the full 
insertion or withdrawal of the CR. However, the \textit{differential CRW} is the
reactivity inserted per unit of withdrawal [pcm/cm]. To calculate those 
parameters, we varied the position of CR clusters from fully withdrawn to 
fully inserted. Equation~\ref{Equ:4} is used to calculate the integral CRW 
[pcm], where $k_{j-1}$ and $k_{j}$ are the effective multiplication factors 
before and after CR insertion to the $j$$^{th}$ step, respectively, and $N$ is the number of steps:

\begin{equation}
\label{Equ:4}
{{\Delta}{\rho}_{j}}=\sum_{j=1}^{N}\dfrac{{k_{j}}-{k_{j-1}}}{{{k_{j}}{k_{j-1}}}}.
\end{equation}

@@

\begin{equation}
\label{Equ:5}
\dfrac{{\partial}{\rho}_{j}}{{\partial{Z}}}=\dfrac{1}{{\Delta}{Z}}\dfrac{{k_{j}}-{k_{j-1}}}{{{k_{j}}{k_{j-1}}}}.
\end{equation}
